Understanding fine temporal scale evolutionary dynamics with lineage metrics

### 2018-04-03 paper.tex

%@AML:  It might be nice to wrap this section up with a little bit of a 'call to action'/'why should you care about this as a community'
%@ELD: I am in favor.
In addition to demonstrating a range of metrics that are immediately applicable and useful to digital evolution research, we intend for this work to begin a conversation within the computational evolution community about how we quantify, interpret, and compare observed evolutionary histories. There has been extensive efforts to improve our ability to visualize both lineages and phylogenies [CITATIONS], which are incredibly valuable for building intuitions and qualitatively understanding the dynamics embedded in a population's evolutionary history. However, we are unaware of efforts to formalize a suite of quantitative lineage and phylogeny-related metrics for computation evolution. Indeed, .... % people have done stuff with lineages
% - often a component of a larger experiment-specific analysis or limited to qualitative descriptions/visualizations
% - well-defined metrics not only provide valuable tools for teasing apart evolutionary dynamics, they also facilitate allow us to move away from exclusively qualitative descriptions/understandings of results ==> better quantitative understanding/statistics ==> better hypothesis testing
% - facilitate comparisons among systems. 
% - Something about activity metrics?

@@

% Changing mutation: here's what happens when we change mutation on each problem
\begin{figure*}
\includegraphics[width=7in]{figs/all_mutation_rate.png}
\caption{Values of example metrics across different mutation rates for each of the four problems. All experiments shown here used a tournament size of 4. Circles are medians and vertical lines show inter-quartile range.}
\label{fig:mutation_rate}
\end{figure*}

>>>>

%@AML:  It might be nice to wrap this section up with a little bit of a 'call to action'/'why should you care about this as a community'
%@ELD: I am in favor.
In addition to demonstrating a range of metrics that are immediately applicable and useful to digital evolution research, we intend for this work to begin a conversation within the %computational evolution
artificial life
community about how we quantify, interpret, and compare observed evolutionary histories. There has been extensive efforts to improve our ability to visualize both lineages and phylogenies [CITATIONS], which are %incredibly valuable for building intuitions and qualitatively understanding the dynamics embedded in a population's evolutionary history. However, we are unaware of efforts to formalize a suite of quantitative lineage and phylogeny-related metrics for computation evolution. Indeed, .... % people have done stuff with lineages
% - often a component of a larger experiment-specific analysis or limited to qualitative descriptions/visualizations
% - well-defined metrics not only provide valuable tools for teasing apart evolutionary dynamics, they also facilitate allow us to move away from exclusively qualitative descriptions/understandings of results ==> better quantitative understanding/statistics ==> better hypothesis testing
% - facilitate comparisons among systems. 
% - Something about activity metrics?

@@

% Changing mutation: here's what happens when we change mutation on each problem
\begin{figure}
\includegraphics[width=3.5in]{figs/all_mutation_rate.png}
\caption{Values of example metrics across different mutation rates for each of the four problems. All experiments shown here used a tournament size of 4. Circles are medians and vertical lines show inter-quartile range.}
\label{fig:mutation_rate}
\end{figure}
